Accelerating adaptive ultrasound algorithms using graphics processing units \vspace{0.5cm}

### 2014-01-04 ThesisJP/Introduction/introduction.tex
Change from variable spacing to fixed spacing in author names

\subsection{Paper I}
\textbf{An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}\\
J. I. Buskenes, \textbf{J. P. \AA{}sen}, C.-I. C. Nilsen and A. Austeng\\
{\it IEEE Transactions on Oceanic Engineering, submitted.}\\\\
Summary of paper...

\subsection{Paper II}
\textbf{Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging}\\
\textbf{J. P. \AA{}sen}, J. I. Buskenes, C.-I. C. Nilsen, A. Austeng and S. Holm\\
{\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. 61, no. 1, pp. \todo{add pages}, Jan. 2014.}\\\\
Summary of paper...

\subsection{Paper III}
\textbf{Capon Beamforming and Moving Objects - An Analysis of Lateral Shift-Invariance}\\
\textbf{J. P. \AA{}sen}, A. Austeng and S. Holm\\
{\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, submitted.}
Summary of paper...

\subsection{Paper IV}
\textbf{Adaptive Volume Rendering of Cardiac 3D Ultrasound Images - Utilizing Blood Pool Statistics}\\
\textbf{J. P. \AA{}sen}, E. Steen, G. Kiss, A. Thorstensen and S. I. Rabben\\
{\it Proc. SPIE Medical Imaging 2012, \todo{add pages}.}\\\\
Summary of paper...

\subsection{Paper V}
\textbf{Huygens on Speed: Interactive Simulation of Ultrasound Pressure Fields}\\
\textbf{J. P. \AA{}sen} and S. Holm
{\it Proc. IEEE Ultrasonics Symposium 2012 \todo{add pages}.}\\\\
Summary of paper...

>>>>

\subsection{Paper I}
\textbf{An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}\\
J.\:I.\:Buskenes, \textbf{J.\:P.\:\AA{}sen}, C.-I.\:C.\:Nilsen and A.\:Austeng\\
{\it IEEE Transactions on Oceanic Engineering, submitted.}\\\\
Summary of paper...

\subsection{Paper II}
\textbf{Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging}\\
\textbf{J.\:P.\:\AA{}sen}, J.\:I.\:Buskenes, C.-I.\:C\:Nilsen, A.\:Austeng and S.\:Holm\\
{\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. 61, no. 1, pp. \todo{add pages}, Jan. 2014.}\\\\
Summary of paper...

\subsection{Paper III}
\textbf{Capon Beamforming and Moving Objects - An Analysis of Lateral Shift-Invariance}\\
\textbf{J.\:P.\:\AA{}sen}, A.\:Austeng and S.\:Holm\\
{\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, submitted.}
Summary of paper...

\subsection{Paper IV}
\textbf{Adaptive Volume Rendering of Cardiac 3D Ultrasound Images - Utilizing Blood Pool Statistics}\\
\textbf{J.\:P.\:\AA{}sen}, E.\:Steen, G.\:Kiss, A.\:Thorstensen and S.\:I.\:Rabben\\
{\it Proc. SPIE Medical Imaging 2012, \todo{add pages}.}\\\\
Summary of paper...

\subsection{Paper V}
\textbf{Huygens on Speed: Interactive Simulation of Ultrasound Pressure Fields}\\
\textbf{J.\:P.\:\AA{}sen} and S.\:Holm\\
{\it Proc. IEEE Ultrasonics Symposium 2012 \todo{add pages}.}\\\\
Summary of paper...

### 2014-01-04 ThesisJP/Thesis.tex
Change from variable spacing to fixed spacing in author names

This thesis is based on the following five papers, referred to in the text by their Roman numerals (I-V): 
\begin{enumerate}[I]
\renewcommand\labelenumi{\bfseries\theenumi}
	\item J. I. Buskenes, \textbf{J. P. \AA{}sen}, C.-I. C. Nilsen and A. Austeng, "An optimised GPU implementation of the MVDR beamformer for active sonar imaging", {\it  IEEE Transactions on Oceanic Engineering, submitted}.
	\item \textbf{J. P. \AA{}sen}, J. I. Buskenes, C.-I. C. Nilsen, A. Austeng and S. Holm, "Implementing Capon beamforming on a GPU for real-time cardiac ultrasound imaging", {\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. 61, no. 1, pp. \todo{add pages} Jan 2014}.
 	\item \textbf{J. P. \AA{}sen}, A. Austeng and S. Holm, "Capon beamforming and moving objects - An analysis of lateral shift-invariance", {\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, submitted}.
	\item \textbf{J. P. \AA{}sen}, E. Steen, G. Kiss, A. Thorstensen and S. I. Rabben, "Adaptive volume rendering of cardiac 3D ultrasound images - utilizing blood pool statistics", {\it Proc. SPIE Medical Imaging 2012 \todo{add pages}}.
	\item \textbf{J. P. \AA{}sen} and S. Holm, "Huygens on speed: Interactive simulation of ultrasound pressure fields", {\it Proc. IEEE Ultrasonics Symposium 2012 \todo{add pages}}.
\end{enumerate}

@@

	\item \textbf{J. P. \AA{}sen}, J. I. Buskenes, C.-I. C. Nilsen, A. Austeng and S. Holm, "Implementing Capon Beamforming on the GPU for Real-Time Cardiac Ultrasound Imaging", {\it Proc. IEEE Ultrasonics Symposium 2012} \todo{add pages}.

	\item J. I. Buskenes, \textbf{J. P. \AA{}sen}, C.-I. C. Nilsen and A. Austeng, "Adapting the Minimum variance beamformer to a graphics processing unit for active sonar imaging systems", {\it Proc. Meetings on Acoustics 2013} \todo{add pages?}.

	\item G. Kiss, E. Steen, \textbf{J. P \AA{}sen} and H. Torp, "GPU volume rendering in 3D echocardiography: real-time pre-processing and ray-casting", {\it Proc. IEEE Ultrasonics Symposium 2010} \todo{add pages}.

@@

	\item E. S. Br\o{}nstad, \textbf{J. P. \AA{}sen}, H. Torp and G. Kiss, "Visibility driven visualization of 3D cardiac ultrasound data on the GPU", {\it Proc. IEEE Ultrasonics Symposium 2012} \todo{add pages}.
\end{enumerate}

>>>>

This thesis is based on the following five papers, referred to in the text by their Roman numerals (I-V): 
\begin{enumerate}[I]
\renewcommand\labelenumi{\bfseries\theenumi}
	\item J.\:I.\:Buskenes, \textbf{J.\:P.\:\AA{}sen}, C.-I.\:C.\:Nilsen and A.\:Austeng, "An optimised GPU implementation of the MVDR beamformer for active sonar imaging", {\it  IEEE Transactions on Oceanic Engineering, submitted}.
	\item \textbf{J.\:P.\:\AA{}sen}, J.\:I.\:Buskenes, C.-I.\:C.\:Nilsen, A.\:Austeng and S.\:Holm, "Implementing Capon beamforming on a GPU for real-time cardiac ultrasound imaging", {\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. 61, no. 1, pp. \todo{add pages} Jan 2014}.
 	\item \textbf{J.\:P.\:\AA{}sen}, A.\:Austeng and S.\:Holm, "Capon beamforming and moving objects - An analysis of lateral shift-invariance", {\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, submitted}.
	\item \textbf{J.\:P.\:\AA{}sen}, E.\:Steen, G.\:Kiss, A.\:Thorstensen and S.\:I.\:Rabben, "Adaptive volume rendering of cardiac 3D ultrasound images - utilizing blood pool statistics", {\it Proc. SPIE Medical Imaging 2012 \todo{add pages}}.
	\item \textbf{J.\:P.\:\AA{}sen} and S.\:Holm, "Huygens on speed: Interactive simulation of ultrasound pressure fields", {\it Proc. IEEE Ultrasonics Symposium 2012 \todo{add pages}}.
\end{enumerate}

@@

	\item \textbf{J.\:P.\:\AA{}sen}, J.\:I.\:Buskenes, C.-I.\:C.\:Nilsen, A.\:Austeng and S.\:Holm, "Implementing Capon Beamforming on the GPU for Real-Time Cardiac Ultrasound Imaging", {\it Proc. IEEE Ultrasonics Symposium 2012} \todo{add pages}.

	\item J.\:I.\:Buskenes, \textbf{J.\:P.\:\AA{}sen}, C.-I.\:C.\:Nilsen and A.\:Austeng, "Adapting the Minimum variance beamformer to a graphics processing unit for active sonar imaging systems", {\it Proc. Meetings on Acoustics 2013} \todo{add pages?}.

	\item G.\:Kiss, E.\:Steen, \textbf{J.\:P.\:\AA{}sen} and H.\:Torp, "GPU volume rendering in 3D echocardiography: real-time pre-processing and ray-casting", {\it Proc. IEEE Ultrasonics Symposium 2010} \todo{add pages}.

@@

	\item E.\:S.\:Br\o{}nstad, \textbf{J.\:P.\:\AA{}sen}, H.\:Torp and G.\:Kiss, "Visibility driven visualization of 3D cardiac ultrasound data on the GPU", {\it Proc. IEEE Ultrasonics Symposium 2012} \todo{add pages}.
\end{enumerate}
